MLISA: Machine Learning-based \\ Intelligent Service Agents

### 2014-11-12 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

abs

@@

The advantages of community of Web services is that the community facilitates the discovery of web services and as community provides better quality services compared to passive models with individual components. In other words, communities act as abstract web services, communicating with external entities via same standard protocols that a normal web services employs. But they requlate the service process via sophisticated internal communication protocols that result in providing a service out of combined work of a number of web services. The down side to communities is the management complexity that involves finding/inviting individual web services and managing the overall quality as combined work done by web services that although have similar functionality, but have different attitudes. Interacting with communities of web services, users send their requests to the coordinators of the community, which plays the role of the community representative or access point. The com munity coordinator in \emph{community centralized} architecture is responsible for task recieve/delivery issues. Moreover, as community representative, it verifies credentials of new web services before accepting them to join the community as well as firing web services, which do not add enough value to the community.

>>>>

Web services are loosely-coupled business applications willing to cooperate in distributed settings within different groups called communities. Communities aim to provide web services with better visibility, efficiency, market share and total payoff. A number of mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities. However, the solutions mostly focus on short term goals and the decisions are optimized for short-term goals. Moreover, these solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion. In this paper, we propose a strategic decision making mechanism that regulates web service agents' decision making process in terms of cooperating with one another. This model first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. 
%Utilizing the training model, the decision making mechanism implements a decision tree with an estimation of long-term utility gain for the web services. Communities can used the trained model and instantly choose best-response strategies considering their long-term gain. 
Our findings show that communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as a single web service can find best communities to target joining them. In further details, after being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions while inviting a web service to join or accepting a join inquiry initiated from a web service. In general, MLISA equips web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore opting for best decision available. The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.

@@

The advantages of community of Web services is that the community facilitates the discovery of web services and as community provides better quality services compared to passive models with individual components. In other words, communities act as abstract web services, communicating with external entities via same standard protocols that a normal web services employs. But they regulate the service process via sophisticated internal communication protocols that result in providing a service out of combined work of a number of web services. The down side to communities is the management complexity that involves finding/inviting individual web services and managing the overall quality as combined work done by web services that although have similar functionality, but have different attitudes. Interacting with communities of web services, users send their requests to the coordinators of the community, which plays the role of the community representative or access point. The com munity coordinator in \emph{community centralized} architecture is responsible for task receive/delivery issues. Moreover, as community representative, it verifies credentials of new web services before accepting them to join the community as well as firing web services, which do not add enough value to the community.
